\begin{thebibliography}{99}

		\bibitem{article2}J. Al Dallal, P. Sorenson, “System testing for object-oriented frameworks using hook technology”, Proceedings 17th IEEE International Conference on Automated Software Engineering, 2002.
		
		\bibitem{article3}Xiaowei Qin, Shuang Tang, Xiaohui Chen, Dandan Miao, Guo Wei, “SQoE KQIs anomaly detection in cellular networks: Fast online detection framework with Hourglass clustering”, China Communications, pp.25-37, 2018.
		
		\bibitem{article4}Pei Yang, Weidong Jin, Peng Tang, “Anomaly Detection of Railway Catenary Based on Deep Convolutional Generative Adversarial Networks”, 2018 IEEE 3rd Advanced Information Technology, Electronic and Automation Control Conference (IAEAC), 2018.
				
		\bibitem{article6}Daojing He, Sammy Chan, Xiejun Ni, Mohsen Guizani, “Software-Defined-Networking-Enabled Traffic Anomaly Detection and Mitigation”, IEEE Internet of Things Journal, 2017.
		
		\bibitem{article7}Vania Bogorny, Shashi Shekhar, “Spatial and Spatio-temporal Data Mining”, 2010 IEEE International Conference on Data Mining, 2010.
		
		\bibitem{article8}Hetal Thakkar, Barzan Mozafari, Carlo Zaniolo, “A Data Stream Mining System”, 2008 IEEE International Conference on Data Mining Workshops, 2008.

		\bibitem{article9}G. Williams, R. Baxter, Hongxing He, S. Hawkins, Lifang Gu, “A comparative study of RNN for outlier detection in data mining”, 2002 IEEE International Conference on Data Mining, 2002. Proceedings, 2002.
		
		\bibitem{article10}A. R. Jakhale, “Design of anomaly packet detection framework by data mining algorithm for network flow”, 2017 International Conference on Computational Intelligence in Data Science (ICCIDS), 2017.
		
		\bibitem{article11}Alireza Tajary, Hamid R. Zarandi, “An Efficient Soft Error Detection in Multicore Processors Running Server Applications”, 2016 24th Euromicro International Conference on Parallel, Distributed, and Network-Based Processing (PDP), 2016.
		
		\bibitem{article14}Chihiro Sakazume, Hiroyuki Kitagawa, Toshiyuki Amagasa, “DIO: Efficient interactive outlier analysis over dynamic datasets”, 2017 Twelfth International Conference on Digital Information Management (ICDIM), 2017.

		\bibitem{article20}Nan Cao, Chaoguang Lin, Qiuhan Zhu, Yu-Ru Lin, Xian Teng, Xidao Wen, “Voila: Visual Anomaly Detection and Monitoring with Streaming Spatiotemporal Data”, IEEE Transactions on Visualization and Computer Graphics, pp. 23 – 33, 2018.
		
		\bibitem{article21}Cheong Hee Park, “Anomaly Pattern Detection on Data Streams”, 2018 IEEE International Conference on Big Data and Smart Computing (BigComp), 2018.
		
		\bibitem{article22}Li Xinran, “Research on massive data 3D-visualization”, 2012 IEEE International Conference on Computer Science and Automation Engineering, 2012.
		
		\bibitem{article23}Y.B. Luo, B.S. Wang, Y.P. Sun, B.F. Zhang, X.M. Chen, “FL-LPVG: An approach for anomaly detection based on flow-level limited penetrable visibility graph”, 2013 International Conference on Information and Network Security (ICINS 2013), 2013.
		
		\bibitem{article24}Hongbin Xia, Wenbo Xu, “Research on Method of Network Abnormal Detection Based on Hurst Parameter Estimation”, 2008 International Conference on Computer Science and Software Engineering, 2008.
		
		\bibitem{article25}Zhixin Sun, Jin Gong, “Anomaly Traffic Detection Model Based on Dynamic Aggregation”, 2010 Third International Symposium on Electronic Commerce and Security, 2010.
		
		\bibitem{article26}Yong Li, Wei-Yi Liu, “Backward probabilistic logic reasoning algorithm for decision problem with Conditional Event ALgebra on Bayesian networks”, 2008 International Conference on Machine Learning and Cybernetics, 2008.
		
		\bibitem{article27}Josef Kittler, William Christmas, Teófilo de Campos, David Windridge, Fei Yan, John Illingworth, Magda Osman, “Domain Anomaly Detection in Machine Perception: A System Architecture and Taxonomy”, IEEE Transactions on Pattern Analysis and Machine Intelligence, pp.845-859, 2014.

		
	\end{thebibliography}